Verifying Spatial Properties of Stencil Computations

### 2016-11-16 paper.tex
Restore origin of region names citation
Cite Cilk and solve author? problem by switching style to plainnat

\bibliographystyle{plain}

@@

Region constants specify a finite contiguous region in a
single dimension relative to the origin and are either \term{pointed},
\term{forward}, \term{backward}, or \term{centered}.  Each region
constant has a dimension identifier $d$ given as a positive natural number.
Each constant except \term{pointed} has a depth
parameter $n$ given as a positive natural number; \term{pointed}
regions implicitly have a depth of $0$.

@@

% Pochoir
\citet{Tang:2011:SPAA} define a specification language for writing
stencils embedded in C++ (with Cilk extensions) that are then compiled
into fast parallel programs based on trapezoidal decompositions with
hyperspace cuts. The Pochoir specification language is used for
describing the kernel, boundary conditions and shape of the
stencil. Programs are first compiled in C++ with a template library
that checks whether the annotations are used correctly, and then a
Pochoir preprocessor may be applied to generate the high-performance
parallel versions using Cilk.  Pochoir
is aimed primarily at assisting programmers who may be reluctant to
implement the high-performance tricky cache-oblivious
``hypertrapezoidal'' algorithms for stencils. 
%that are significantly faster than the typical looping implementations
%of stencil computations.
Like much of the related work, the main goal 
is optimisation rather than verifying program correctness.

>>>>

\bibliographystyle{plainnat}

@@

Region constants specify a finite contiguous region in a
single dimension relative to the origin and are either \term{pointed},
\term{forward}, \term{backward}, or \term{centered}. The region names are
inspired by the scientific terminology, \eg{} the standard explicit method for
approximating PDEs is known as the \emph{Forward Time, Centered Space} (FTCS)
scheme~\citep{dawson1991finite}. Each region
constant has a dimension identifier $d$ given as a positive natural number.
Each constant except \term{pointed} has a depth
parameter $n$ given as a positive natural number; \term{pointed}
regions implicitly have a depth of $0$.

@@

% Pochoir
\citet{Tang:2011:SPAA} define a specification language for writing
stencils embedded in C++ (with Cilk~\citep{blumofe1996cilk} extensions) that
are then compiled
into fast parallel programs based on trapezoidal decompositions with
hyperspace cuts. The Pochoir specification language is used for
describing the kernel, boundary conditions and shape of the
stencil. Programs are first compiled in C++ with a template library
that checks whether the annotations are used correctly, and then a
Pochoir preprocessor may be applied to generate the high-performance
parallel versions using Cilk.  Pochoir
is aimed primarily at assisting programmers who may be reluctant to
implement the high-performance tricky cache-oblivious
``hypertrapezoidal'' algorithms for stencils. 
%that are significantly faster than the typical looping implementations
%of stencil computations.
Like much of the related work, the main goal 
is optimisation rather than verifying program correctness.
